One more attempt on ArXe

### 2015-03-18 exp_results.tex
ruledtabular raus
1004 values added, changed

\section{Experimental Results}
\begin{table}
\caption{
Expansion parameters used in this work for cluster production. All clusters were produced with a $d = 80~\mu$m conical nozzle of 15$^\circ$ half opening angle. For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given. These values are calculated as in ref.\ \protect\citenum{hagena1981}. Due to the small amount of Xe admixture, we basically have a Xe seeded expansion of Ar gas. We therefore expect actual cluster sizes in-between the two limiting values given. Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model used.
\label{tab:cluster} }

\begin{ruledtabular}
\begin{tabular}{l c c c r r}
%
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\hline
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset berücksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\hline
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\hline
% 1004 842
1004  & 3.0 &  165   & 2.8   & 1220 & 20900\\
% 1004 858
  & 5.0 &  149   & 2.5   & 1620 & 27700\\
%
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}). It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainty are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}. $E_b$ and $w$ are in eV, $A$ is in \%. The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
\label{tab:valence} }
\begin{ruledtabular}
\begin{tabular}{ l c c c c c c}
%
  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
%
\hline
% Ar, from Marko
 Ar (1) &  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar (2) &  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
%
\end{tabular}
\end{ruledtabular}
\end{table}

>>>>

\section{Experimental Results}
\begin{table}
\caption{
Expansion parameters used for cluster production in this work. All experiments were done with a $d = 80~\mu$m conical nozzle of 15$^\circ$ half opening angle. For the mixed clusters, $\langle N_{Ar} \rangle$ and $\langle N_{Xe} \rangle$ refer to hypothetical cluster sizes yielded with an expansion of the respective pure gas at the conditions given. These values are calculated as in ref.\ \protect\citenum{hagena1981}. Due to the small amount of Xe admixture, we basically have a Xe seeded expansion of Ar gas. We therefore expect actual cluster sizes in-between the two limiting values given. Inaccuracies in the calculation of $\langle N\rangle$ due to fluctuations of the input parameters are less than 6\,\%. This figure does not include systematic errors of the empirical model used.
\label{tab:cluster} }

\begin{tabular}{l c c c r r}
%
\toprule
  label  &  Xe$_{in}$ [\%]  &  $T$ [K]  &  $p$ [bar] & $\langle N_{Ar} \rangle$ & $\langle N_{Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar (1)  & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar (2)  & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
 (a) & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
 (b) & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
 (c) & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
 (d) & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
 (e) & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe (1)  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
1103, only coinc  & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
  & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 858
858  & 5.0 &  149   & 2.50  & 1620 & 27700\\
% 1004 867
867  & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
868  & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886
886  & 2.5 &  161   & 2.41  &  980 & 16770\\
%
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $E_b$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters always is higher than in the original gas mixture (see Tab.\ \protect\ref{tab:cluster}). It was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainty are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. Labels given in the first column refer to the expansion parameters in Tab.\ \protect\ref{tab:cluster}. $E_b$ and $w$ are in eV, $A$ is in \%. The binding energies can be compared to atomic values of 15.82~eV, 13.43~eV and 12.13~eV for Ar 3p and Xe 5p.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c}
%
\toprule
  label & $E_b$(Ar 3p) & $w$(Ar 3p) & $E_b$(Xe 5p$_{1/2}$) &  $E_b$(Xe 5p$_{3/2}$) & $w$(Xe 5p$_{3/2}$)  &  $A$(Xe) \\
%
\midrule
% Ar, from Marko
 Ar (1) &  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar (2) &  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 (a) & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 (b) & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 (c) & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 (d) & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 (e) & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
Xe (1) & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 556 & 15.12 & 1.3 & 12.44 & 10.70 & 1.24 & 19\\
\bottomrule
\end{tabular}
\end{table}
